The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191025.tex
CIV tex/ tidy up

% \hypersetup{draft}

@@

  \begin{tabular}{r  l  r r r   r r r r}

@@

    Object                           & \multirow{3}{*}{Redshift}  & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
    R.A. / deg                     &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
    Decl. / deg                   &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\

@@

    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &                            & 2089-427             & \\
    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions? \\
    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\

@@

    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &                               &  2948-614              & \\

@@

    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  2$\times$900    &                              & \\

@@

    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &                             &   7582-790          & QSO1-REOBS \\ 
    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2$\times$1200  &                           &    \\

@@

@@

%%   B a c k g r o u n d     L i t e r a t u r e    
\civ\ variability has been long studied, e.g., \citet[][]{Baldwin1977,
Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
Laor1995, McIntosh1999, Nazarova2003}.  \citet{Wilhite2006} examine
the variability of a C~\textsc{iv} sample of 105 quasars observed at
multiple epochs by the SDSS.  They find a strong correlation between
the change in the C~\textsc{iv} line flux and the change in the line
width, but no correlations between the change in flux and changes in
line center and skewness.  These authors find that the relation
between line flux change and line width change is consistent with a
model in which a broad line base varies with greater amplitude than
the line core. The C~\textsc{iv} lines in these high-luminosity
quasars appear to be less responsive to continuum variations than
those in lower luminosity AGN.  \citet{Wilhite2006} find no evidence
for variability of the well known blueshift of the C~\textsc{iv} line
with respect to the low-ionization Mg~\textsc{ii}$\lambda$2798 line in
the highest flux objects.

@@

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.0cm  0.2cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20190920.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings given by the vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. These SDSS, BOSS and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
(DBSP) instrument on the Palomar {\it Hale} 5m telescope.

@@

 When using the \citet{Shen2011} catalogue, we report line luminosity,
FWHM, rest-frame equivalent width, and their errors for the {\it
whole} \mgii profile (this catalogue also quotes values for just the
broad \mgii component, but the differences for our objects is
negligible). The line luminosities in \citet{Calderone2017} are given
in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
\citet{Shen2011} are in units of $\log(L)$.  We do not report
the \citet{Shen2011} error on the line luminosity.

Power-law continuum slopes, $\alpha_{\lambda}$ where $f_{\lambda}
\propto \lambda^{\alpha}$, are also reported in these catalogues and
from QSFit.  We quote the most appropriate value given the emission
line wavelength.

\subsection{Multi-wavelength properties}
We use data from the beginning of the WISE mission \citep[2010
January; ][]{Wright2010} through the fifth-year of NEOWISE-R
operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
pattern leads to coverage of the full-sky approximately once every six
months (a ``sky pass''), but the satellite was placed in hibernation
in 2011 February and then reactivated in 2013 October. Hence, our
light curves have a cadence of 6 months with a 32 month sampling gap.
%Radio ??

@@

For J1205+3422, over the course of 5040 days observed, 1640 days in
the rest-frame.  For J1638+2827, over the course of 1279 days
observed, 400 days in the rest-frame, the broad \civ\ and \ciii BEL
start to fade.  For J2228+2201, over the course of 771 days observed,
240 days in the rest-frame, broad \civ\ and \ciii BELs both emerge and
the standard UV/blue continuum slope increases in flux.  the UV/blue
continuum diminishes and the shape of \lya changes.

@@

                                              & 58538     & \lya      & 1393$\pm$11   & $>$15000            &  $-796\pm57$           &  ---                         &  ---                        &   QSFit  \\
    \rowfont{\color{blue}}        & 58538     & \civ      & 1037$\pm$5    & $>$15000            &  983$\pm$40             &  ---                         &  ---                         &   QSFit    \\  
                                              & 58538      & \ciii     &   677$\pm$4    & $>$15000            & $>$3000                     &  ---                         &  ---                         &  QSFit   \\  
    \rowfont{\color{teal}}         & 58538     & \mgii    &  755$\pm$4    & $>$15000            & 350$\pm$39               &  ---                         &  ---                         &   QSFit  \\

@@

                                              & 58693      & \lya     &  290$\pm$3        & 8803$\pm$52     &  $-1096\pm35$        &  ---                        & $<$-3                      &   QSFit  \\
    \rowfont{\color{blue}}        & 58693     & \civ      &   68$\pm$0.9     & 3743$\pm$26     &   591$\pm$17           &   ---                       & $<$-3                       &  QSFit   \\  
                                              & 58693      & \ciii     &   19$\pm$0.4     & 5625$\pm$         &   $>$3000                  &    ---                      & $<$-3                      &  QSFit    \\  
    \rowfont{\color{teal}}         & 58693     & \mgii    &   19$\pm$0.4    & 1530$\pm$22     &  $>$3000                   &    ---                        &$<$-3                      &  QSFit   \\  

@@

      \rowfont{\color{blue}}        & 58583      & \civ      &  659$\pm$5   & $>$15000                &  $-493\pm56$          &   333$\pm$3            & $-0.43\pm0.01$     &   QSFit   \\  
                                                & 58583      & \ciii      &  239$\pm$4   &  $>$15000               &  1514$\pm$127        &  124$\pm$2             & $-0.43\pm0.01$     &   QSFit   \\   
    \rowfont{\color{teal}}           & 58583      & \mgii   &  129$\pm$3    &  10957$\pm$307    &  138$\pm$128          &   78$\pm$2              &  $-0.43\pm0.01$    &   QSFit   \\  

@@

                                               & 56960    & \ciii      & 185$\pm$5         &        -                       &  2701$\pm$225     &   47.75$\pm$1.29      &  &   QSFit    \\  
   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340     &   188$\pm$137      &   50.75$\pm$2.21     &   &   QSFit   \\

@@

%   
     \rowfont{\color{blue}}        & 58693    & \civ     &  327$\pm$1          &  $>$15000              &   $-453\pm34$     &   ---                           & ---  &   QSFit   \\  
                                               & 58693    & \ciii      & 115.08$\pm$1.2  &  $>$15000              &  2422$\pm$67       &   ---                          & ---  &   QSFit   \\  
     \rowfont{\color{teal}}         & 58693    & \mgii   & 46.361$\pm$1.3   &  $>$15000             &  $>$1000                &   ---                          & ---  &   QSFit   \\  

@@

\begin{itemize}
  \item {SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.}
\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
\item Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z>2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
\item 
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim10\%$ in Eddington luminosity.
\end{itemize}

>>>>

\hypersetup{draft}

@@

  \begin{tabular}{r l   r ll   r r r r}

@@

    Object                           & \multirow{3}{*}{Redshift}  &                       & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date} & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
    R.A. / deg                     &                                         &   {$g$-band}   &                                 &                                  &                                               &  Time           & Spectrum                 & \\
    Decl. / deg                   &                                         &    magnitude   &                                &                                   &                                              &  / seconds    & Plate-FiberID  & \\

@@

    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &  8057                  & 2089-427             & \\
    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  1800                  &  ---                      &  Average conditions \\
    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2400                   &  ---                      &   \\

@@

    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &   4801                    &  2948-614              & \\

@@

    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  1800                   &  ---                             & \\

@@

    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\ 
    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2400                   &    ---                        &    \\

@@

    %  2019-Feb-24    & DBSP            &  2$\times$900 f
    %  2019-Jul-29     & DBSP            &  2$\times$1200
    %  2019-Apr-10     & LRIS              &  2$\times$900
    %& 2019-Jul-29       & DBSP             & 2$\times$1200

@@

%%   B a c k g r o u n d     L i t e r a t u r e    
\civ\ variability has been long studied, e.g., \citet[][]{Baldwin1977,
Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
Laor1995, McIntosh1999, Nazarova2003}.

\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
of 105 quasars observed at multiple epochs by the Sloan Digital Sky
Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
find a strong correlation between the change in the C~\textsc{iv} line
flux and the change in the line width, but no correlations between the
change in flux and changes in line center and skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  \citet{Wilhite2006}
find no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.

@@

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191024.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191024.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191024.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings given by the vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. The SDSS, BOSS and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
(DBSP) instrument on the Palomar {\it Hale} 5m telescope.

@@

When using the \citet{Shen2011} catalogue, we report line luminosity,
FWHM, rest-frame equivalent width, and their errors for the whole
\mgii profile (this catalogue also quotes values for just the broad
\mgii component, but the differences for our objects is
negligible). The line luminosities in \citet{Calderone2017} are given
in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
\citet{Shen2011} are in units of $\log(L)$.  We do not report the
\citet{Shen2011} error on the line luminosity.

Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.  We quote the most appropriate value given the emission line
wavelength.

\subsection{Multi-wavelength properties}
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning of the
Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
January; ][]{Wright2010} through the fifth-year of NEOWISE-R
operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
pattern leads to coverage of the full-sky approximately once every six
months (a ``sky pass''), but the satellite was placed in hibernation
in 2011 February and then reactivated in 2013 October. Hence, our
light curves have a cadence of 6 months with a 32 month sampling gap.
%Radio ??

@@

For J1205+3422, our spectral observations cover 5195 days observed, 1691 days
in the rest-frame. For J1205+3422 is identified in SDSS as a bright
$g\approx18.0$, blue-sloped quasar with broad \siiv, \civ, \ciii and
\mgii observed in the initial spectrum (MJD 53498; 2005-May-08). \ciii
and \civ\ are seen to have large blueshifts of $\approx$2600$\pm$150
and $\approx$1150$\pm$100 km s$^{-1}$, respectively.  By the time the
2019 spectra were taken (MJD 58538, 2019-Feb-24 and MJD 58693
2019-Jul-29), however, the light curve has dropped by $\sim$1.5
magnitudes and the spectra are significantly less steep.  While \lya
and \nv are detectable in both the MJD 58538 and MJD 58693 DBSP
spectra, \civ\ has all but disappeared in the MJD 58693 spectrum.  The
broad \ciii emission has disappeared between the 2005 and 2019
spectra. {\it The changes in \civ\ and \ciii going from broad emission to
barely detectable have on the timescales of $\approx$50 days in the rest-frame.}

For J1638+2827, our spectral observations cover 4030 days observed, 1265 days
in the rest-frame. Here, in the initial epoch spectrum, \civ\ is broad
and bright, as is \ciii. However, just over 400 days in the rest-frame
later, the broad \civ\ and \ciii BEL have to faded, the continuum
slope around 1400\AA\ has changed from $\approx$-1.48 to
$\approx$-2.25, but the \lya/\nv emission complex is very similar in
shape and line flux intensity. Around 870 days in the rest-frame after
the second spectral epoch, \lya, \nv, \civ, \ciii and \mgii are all
apparent and broad, with \mgii being seen for the first time at high
signal-to-noise. The light curve is consistent with this spectral
brightening, increasing from around $\sim$19.5-20.5th magnitude to
$\sim$18.5 in the optical band. An absorption feature between  \lya and \nv
is seen in all three spectral epochs.

For J2228+2201, our spectral observations cover 2504 days observed,
778 days in the rest-frame. Over the course of 240 days in the rest-frame, \civ\ and \ciii both {\it emerge} as BELs and
the standard UV/blue continuum slope increases in flux.
Then, over the course of 538 days in the rest-frame, the broadline emission, while still
very present, reduces in line flux the UV/blue continuum diminishes,
though is still more luminous than the initial BOSS spectrum.

@@

                                            & 58538     & \lya      & 1393$\pm$11   & $>$15000            &  $-796\pm57$          &  ---                        &  ---                       &   QSFit (NPR) \\
                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit (MJG) \\
   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit (NPR)   \\
    \rowfont{\color{blue}}      & 58538     & \civ      &       0$\pm$-    & 14995$\pm$0       & $>$3000$\pm$         &  ---                       &  ---                       &   QSFit (MJG)    \\  
                                            & 58538      & \ciii     &  677$\pm$4     & $>$15000             & $>$3000                    &  5770$\pm$34       &  ---                       &  QSFit  (NPR) \\  
                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit (MJG)  \\
    \rowfont{\color{teal}}      & 58538     & \mgii    &  755$\pm$4     & $>$15000            & 350$\pm$39               &  7571$\pm$37       &  ---                       &   QSFit (NPR) \\
    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit (MJG) \\

@@

                                           & 58693     & \lya     &  290$\pm$3       & 8803$\pm$52     &  $-1096\pm35$        &  ---                           & $<$-3                   &   QSFit  (NPR)\\
                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  (MJG) \\ 
    \rowfont{\color{blue}}    & 58693     & \civ      &   68$\pm$0.9    & 3743$\pm$26     &   591$\pm$17           &   ---                           & $<$-3                   &  QSFit   (NPR)\\  
    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit  (MJG)  \\  
                                           & 58693     & \ciii     &   19$\pm$0.4    & 5625$\pm$          &   $>$3000                 &  988$\pm$20             & $<$-3                   &  QSFit   (NPR) \\  
                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   (MJG)  \\  
   \rowfont{\color{teal}}      & 58693     & \mgii    &  19$\pm$0.4    & 1530$\pm$22      &  $>$3000                  &    499$\pm$9             &$<$-3                    &  QSFit (NPR)  \\
   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit  (MJG)  \\  

@@

                                               & 58583       & \lya    &  1086$\pm$14  & $>$15000     	&   $-1047\pm88$        &  500$\pm$6   	  & $-0.443\pm0.01$   & QSFit  (NPR)\\ 
                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          & QSFit  (MJG) \\
   \rowfont{\color{blue}}         & 58583      & \civ      &  659$\pm$5     & $>$15000                &  $-493\pm56$          &   333$\pm$3           & $-0.43\pm0.01$     &   QSFit (NPR)  \\
   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit (MJG)  \\  
                                               & 58583      & \ciii      &  239$\pm$4    &  $>$15000               &  1514$\pm$127        &  124$\pm$2            & $-0.43\pm0.01$     &   QSFit  (NPR) \\   
                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit   (MJG) \\   
   \rowfont{\color{teal}}           & 58583      & \mgii   &  129$\pm$3    &  10957$\pm$307    &  138$\pm$128          &   78$\pm$2              & $-0.43\pm0.01$     &   QSFit  (NPR) \\
   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit    (MJG) \\  

@@

                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\  
   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\

@@

                                               & 58693     & \lya      &  228$\pm$3       & 4279$\pm$32       &   $-1000\pm29$     &  91976$\pm$1311  &  ---                       & QSFit  (NPR)\\ 
                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &    QSFit  (MJG) \\
     \rowfont{\color{blue}}        & 58693     & \civ      &  327$\pm$1      &  $>$15000             &   $-453\pm34$       &  20298$\pm$106    & ---                        & QSFit   (NPR)\\  
     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit (MJG)  \\  
                                               & 58693     & \ciii      & 269$\pm$1.5    &  $>$15000             &  2302$\pm$42.6     &   3776$\pm$21      & ---                          &  QSFit  (NPR) \\
                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit (MJG)   \\  
     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit (NPR) \\
     \rowfont{\color{teal}}        & 58693     & \mgii    &  89$\pm$1.4     &  $>$15000             &  $>$1000                &   1230$\pm$1.9    & ---                            &   QSFit  (MJG) \\  

@@

\begin{itemize}
  \item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
\item Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z>2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
\item 
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim10\%$ in Eddington luminosity.
\end{itemize}
